Supplementary Material for ``Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)"

### 2023-07-30 ba_resubmit_template_files/supplement.tex
fix typos using antidote 11.

%\documentclass[ba]{imsart}
%% use command below for supplement
 \documentclass[ba,preprint]{imsart}
%
\pubyear{2021}
\volume{TBA}
\issue{TBA}
% \doi{0000}
%\arxiv{}
\firstpage{1}
\lastpage{1}

@@

	We provide detailed derivations of the full-conditionals provided in Section \ref{sec:fast-beta-linkage}. The $\bm{m}$ and $\bm{u}$ parameters are updated through standard multinomial-Dirichlet distributions. For a particular $m_{fl}$, we have
	\begin{align}
		\mathcal{L}(m_{fl}|\gamma, \bm{u}, \bm{Z}, \pi) &\propto \prod_{i=1}^{n_A} \prod_{j=1}^{n_B} m_{fl}^{I(Z_j = i) I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}  m_{fl}^{\alpha_{fl} - 1} = m_{fl}^{\alpha_{fl}(\bm{Z}) - 1},
	\end{align}
	where $\alpha_{fl}(\bm{Z})= \alpha_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j = i)$. Analogous procedures lead to $\mathcal{L}(u_{fl}| \gamma, \bm{m}, \bm{Z}, \pi)$  $\propto u_{fl}^{\beta_{fl}(\bm{Z}) - 1}$, where $\beta_{fl}(\bm{Z})= \beta_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j \neq i)$. Thus, for the vectors of parameters $\bm{m}_f$ and $\bm{u}_f$, we have
	\begin{align}
	\bm{m}_f^{(s+1)} |
	\gamma, 
	\bm{Z}^{(s)}, \bm{u}^{(s)}, \pi^{(s)} &\sim 
	\text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \\
	\bm{u}_f^{(s+1)} | \gamma, \bm{Z}^{(s)}, \bm{m}^{(s)}, \pi^{(s)} &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})).
	\end{align}

@@

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
			\caption{Representative traceplot of overlap between files from simulation study in Section \ref{accuracy}.}\label{fig:sim_overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
			\caption{Representative traceplot of $\bm{m}$ parameter from simulation study in Section \ref{accuracy}.}\label{fig:sim_m_trace}
		\end{center}

@@

		\begin{table}[h]
		\centering
		\begin{tabular}{llll|lll}
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{$\bm{m}$} & \multicolumn{3}{c}{$\bm{u}$} \\
			\cline{2-4} \cline{5-7}
			& Agree & Partial & Disagree & Agree & Partial & Disagree \\
			\hline
			Feature 1 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 2 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 3 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 4 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			\hline
		\end{tabular}
		\caption{Probabilities used for $\bm{m}$ and $\bm{u}$ distributions in simulation study in Supplement \ref{app:appendix-speed}.}\label{Tab:distributions_2}
	\end{table}

@@

@@

	\bibliographystyle{jasa}
	\bibliography{fabl}

>>>>

%\documentclass[ba]{imsart}
%% use command below for supplement
 \documentclass[ba,preprint]{imsart}
%
\pubyear{2023}
\volume{TBA}
\issue{TBA}
% \doi{0000}
%\arxiv{}
\firstpage{1}
\lastpage{1}

@@

	We provide detailed derivations of the full conditionals provided in Section \ref{sec:fast-beta-linkage}. The $\bm{m}$ and $\bm{u}$ parameters are updated through standard multinomial-Dirichlet distributions. For a particular $m_{fl}$, we have
	\begin{align}
		\mathcal{L}(m_{fl}|\gamma, \bm{u}, \bm{Z}, \pi) &\propto \prod_{i=1}^{n_A} \prod_{j=1}^{n_B} m_{fl}^{I(Z_j = i) I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}  m_{fl}^{\alpha_{fl} - 1} = m_{fl}^{\alpha_{fl}(\bm{Z}) - 1},
	\end{align}
	where $\alpha_{fl}(\bm{Z})= \alpha_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j = i)$. Analogous procedures lead to $\mathcal{L}(u_{fl}| \gamma, \bm{m}, \bm{Z}, \pi)$  $\propto u_{fl}^{\beta_{fl}(\bm{Z}) - 1}$, where $\beta_{fl}(\bm{Z})= \beta_{fl} + \sum_{i=1}^{n_A}  \sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f)I(\gamma_{ij}^f = l) I(Z_j \neq i)$. Thus, for the vectors of parameters $\bm{m}_f$ and $\bm{u}_f$, we have
	\begin{align}
	\bm{m}_f^{(s+1)} |
	\gamma, 
	\bm{Z}^{(s)}, \bm{u}^{(s)}, \pi^{(s)} &\sim 
	\text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \\
	\bm{u}_f^{(s+1)} | \gamma, \bm{Z}^{(s)}, \bm{m}^{(s)}, \pi^{(s)} &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})).
	\end{align}

@@

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_overlap_trace} 
			\caption{Representative traceplot of overlap between files from simulation study in Section~\ref{accuracy}.}\label{fig:sim_overlap_trace}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sim_m_trace} 
			\caption{Representative traceplot of $\bm{m}$ parameters from simulation study in Section~\ref{accuracy}.}\label{fig:sim_m_trace}
		\end{center}

@@

		\begin{table}[h]
		\centering
		\begin{tabular}{llll|lll}
			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{$\bm{m}$} & \multicolumn{3}{c}{$\bm{u}$} \\
			\cline{2-4} \cline{5-7}
			& Agree & Partial & Disagree & Agree & Partial & Disagree \\
			\hline
			Feature 1 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 2 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 3 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			Feature 4 & $\frac{9}{10}$ & $\frac{9}{100}$  & $\frac{1}{100}$ & $\frac{1}{100}$ &  $\frac{3}{100}$ & $\frac{96}{100}$ \\ 
			\hline
		\end{tabular}
		\caption{Probabilities used for $\bm{m}$ and $\bm{u}$ distributions in simulation study in Supplement~\ref{app:appendix-speed}.}\label{Tab:distributions_2}
	\end{table}

@@

%\bibliographystyle{jasa}
%	\bibliography{fabl}

@@
